Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

\begin{equation}
  GDP = \beta_0 + \beta_1 TPEC + \beta_2 TCMR+ \beta_3 DPI + \beta_4 UNRATE + \beta_5 BSPL
\end{equation}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{AVP1}
  \caption{This figure shows the AV Plots for the variables included in Model 1}
\end{figure}

>>>>

\begin{equation}
  GDP = \beta_0 + \beta_1 TPEC + \beta_2 TCMR+ \beta_3 DPI + \beta_4 UNRATE + \beta_5 BSPL +\beta_6 POP
\end{equation}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale = .5]{AVP1}
  \caption{This figure shows the AV Plots for the variables included in Model 1}
\end{figure}

From the output above, it can be concluded that there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP.
A weak linear relationship is show fromthe varibles TPEC and POP with GDP. 
This output confirms that the relationship between TPEC and POP with GDP are not significant in this model.

For the second model, the non significant variables from Model 1 are removed. 
Model 1 was built using the independent variables TCMR, DPI, UNRATE and BSLP from the training dataset. 
The equation used for Model 2 is as follows:

\begin{equation}
  GDP = \beta_0 + \beta_1TCMR+ \beta_2 DPI + \beta_3 UNRATE + \beta_4 BSPL
\end{equation}

Summary statistics for Model 2 are as follows:

\begin{figure}[H]
  \centering
  \includegraphics[scale = .5]{mod2output}
  \caption{This figure shows the output from R for the summary statistics for Model 2}
\end{figure}
